The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2020-03-31 razzo-discussion.tex
Add awesome 20200204 results, with 40 replicates

We \richel{(at least I. If you do not expect this, let me know the 
reasoning why)} expected to find a bigger inference error 
when increasing the amount of co-occurring speciation events.
The reason is simple: the tree prior used assumes speciation does not
co-occur. The stronger the amount of co-occurring speciation, the stronger
the deviation from the species tree prior.

@@

When simulating a DNA alignment, we chose to use the simplest (JC69) site
model and the simplest (strict) clock model. One could argue these models
are overly simplistic and biologically irrelevant. We argue that this
actually improves the clarity of our results for two reasons. The first
reason is a practical one: because the computational load was lowered,
we were able to perform more replicates. For a process with this high
amount of stochaticity, we think this is highly favored. The second reason
is that we think this reduces the noise of our results, without 
hurting the experiment: in our setup, it is essential
to assume the same generative site and clock model as the one that is actually 
used. Sure, we could have generated the alignment with a 
complex (GTR) site model and a complex (relaxed log-normal) clock model, then
correctly assume these were the generative site and clock model.
But that would be besides the point of the experiment: to measure the impact
of the tree prior.

When simulating our phylogenies, we used an MBD model with and without
extinction. In the case in which extinction is present,
picking the BD tree prior as the generative tree prior seems justified:
it is the best-fitting standard tree prior. For the MBD model without
extinction, \richel{@Giappo: I think this is an interesting insight:} 
we could have picked the Yule tree prior. We \richel{at least I do} predicted
that the Yule tree prior will be selected as the best candidate model
more often in this scenario, which shows the sensitity of the method we used.

To compare multiple inference models, we picked the Nested Sampling
approach to directly compare marginal likelihoods. We could have used
alternative methods like \richel{forgot the term for now: where you
do an MCMC that can switch between models}. The reason we used Nested
Sampling was mostly pragmatic and we think other methods are equivalent.

>>>>

We expected to find a bigger inference error 
when increasing the amount of co-occurring speciation events.
The reason is simple: the tree prior used assumes speciation does not
co-occur. The stronger the amount of co-occurring speciation, the stronger
the deviation from the species tree prior.

@@

When simulating a DNA alignment, we chose to use the simplest (JC69) site
model and the simplest (strict) clock model. One could argue these models
are overly simplistic and biologically irrelevant. We argue that this
actually improves the clarity of our results for two reasons. The first
reason is a practical one: because the computational load was lowered,
we were able to perform more replicates. For a process with this high
amount of stochasticity, we think this is highly favored. The second reason
is that we think this reduces the noise of our results, without 
hurting the experiment: in our setup, it is essential
to assume the same generative site and clock model as the one that is actually 
used. Sure, we could have generated the alignment with a 
complex (GTR) site model and a complex (relaxed log-normal) clock model, then
correctly assume these were the generative site and clock model.
But that would be besides the point of the experiment: to measure the impact
of the tree prior.

When simulating our phylogenies, we used an MBD model with and without
extinction. In the case in which extinction is present,
picking the BD tree prior as the generative tree prior seems justified:
it is the best-fitting standard tree prior. For the MBD model without
extinction, we could have picked the Yule tree prior. 
We predicted that the Yule tree prior will be selected as the best candidate model
more often in this scenario, which shows the sensitivity of the method we used.

To compare multiple inference models, we picked the Nested Sampling
approach to directly compare marginal likelihoods. We could have used
alternative methods like \richel{forgot the term for now: where you
do an MCMC that can switch between models}. The reason we used nested
sampling was mostly pragmatic and we think other methods are equivalent.
